---
title: "LAVA Development Guide"
subtitle: "Contributing to the LAVA Package"
author: "Isabela do O"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
  pdf_document:
    toc: true
    number_sections: true
    latex_engine: xelatex
    fig_caption: true
vignette: >
  %\VignetteIndexEntry{LAVA Development Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

This guide provides information for developers who want to contribute to the LAVA package.

## Development Setup

To set up your development environment for LAVA:

1. Clone the repository:
```
git clone https://github.com/isadoo/LAVA.git
```

2. Open the project in RStudio or VS Code with R extension.

3. Install development dependencies:
```{r, eval=FALSE}
install.packages(c("devtools", "roxygen2", "testthat", "knitr", "rmarkdown", "covr"))
```

## Package Structure

The LAVA package follows the standard R package structure:

- `R/`: Contains R code
- `man/`: Documentation (generated by roxygen2)
- `tests/`: Unit tests
- `vignettes/`: Package vignettes
- `data/`: Package data
- `data-raw/`: Scripts to generate package data

## Documentation

Documentation is generated using roxygen2. Make sure to document all exported functions with roxygen comments:

```{r, eval=FALSE}
#' Function Title
#' 
#' @param param1 Description of parameter 1
#' @return Description of return value
#' @export
#' @examples
#' example_function("example")
example_function <- function(param1) {
  # Function implementation
}
```

Generate documentation using:

```{r, eval=FALSE}
devtools::document()
```

## Testing

Write tests for all functions in the `tests/testthat/` directory. Run tests with:

```{r, eval=FALSE}
devtools::test()
```

## Building and Checking

Build the package with:

```{r, eval=FALSE}
devtools::build()
```

Check the package with:

```{r, eval=FALSE}
devtools::check()
```

## Continuous Integration

The package uses GitHub Actions for continuous integration:

- R-CMD-check: Runs R CMD check on multiple platforms
- test-coverage: Checks test coverage
- pkgdown: Builds and deploys the documentation website

## Website

The package documentation website is built using pkgdown and deployed to GitHub Pages.

To build the website locally:

```{r, eval=FALSE}
pkgdown::build_site()
```

## Releasing

To prepare for a release:

1. Update `NEWS.md`
2. Update version number in `DESCRIPTION`
3. Run all checks and tests
4. Create a release on GitHub

## Guidelines for Contributors

- Follow the tidyverse style guide
- Write tests for all functions
- Document all exported functions
- Update NEWS.md for notable changes

## Session Info

```{r}
sessionInfo()
```