---
title: "Introduction to LAVA"
subtitle: "Log ratio of Ancestral Variances Analysis"
author: "Isabela do O"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
    highlight: tango
    code_folding: show
  pdf_document:
    toc: true
    number_sections: true
    latex_engine: xelatex
    fig_caption: true
    includes:
      in_header: !expr if(file.exists("latex_header.tex")) "latex_header.tex"
vignette: >
  %\VignetteIndexEntry{Introduction to LAVA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: !expr if(file.exists("references.bib")) "references.bib"
csl: !expr if(file.exists("style.csl")) "style.csl"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LAVA)
```

## Introduction

LAVA (Log ratio of Ancestral Variances) is an R package designed to help researchers analyze genomic data through the lens of ancestral variance ratios. This vignette provides an introduction to the package's functionality and demonstrates how to use its core features.

## Installation

You can install LAVA from GitHub using:

```{r, eval=FALSE}
# install.packages("pak")
pak::pak("isadoo/LAVA")
```

## Basic Usage

Here's a simple example of how to use LAVA:

```{r example, eval=FALSE}
# Sample code will go here
# This is a placeholder for when the actual functionality is implemented
```

## Advanced Features

This section will cover more advanced features of the LAVA package.

```{r advanced, eval=FALSE}
# Advanced usage examples will go here
# This is a placeholder for when the actual functionality is implemented
```

## Summary

This vignette has provided an overview of the LAVA package. For more detailed information, refer to the function documentation and other vignettes.

## Session Info

```{r}
sessionInfo()
```